### 2016-05-26 Paper_v1.tex
May26

>>>>

%PEP was modeled as an inhibitor for phosphofructokinase \cite{2011_cabrera_JBiolChem}.
%PEP was modeled as an activator for fructose-biphosphatase \cite{2000_donahue_JBacteriol,2006_hines_JBiolChem,2007_hines_JBiolChem}.
%FDP was modeled as an activator for pyruvate kinase \cite{2010_zhu_Biochimie}.
%PEP was modeled as an inhibitor for PEP carboxykinase \cite{2003_ravanal_JProteinChem}.
%FDP was modeled as an activator for PEP carboxylase \cite{1972_wohl_JBiolChem}.
%Pyruvate was modeled as an inhibitor for pyruvate dehydrogenase \cite{2007_kale_JBiolChem,2002_arjunan_Biochemistry}.
%PEP was modeled as an inhibitor for PEP synthetase \cite{1973_chulavatnatol_JBiolChem}.
%AKG was modeled as an inhibitor for citrate synthase \cite{1994_pereira_JBiolChem,1983_robinson_FEBSLett}.
%PEP was modeled as an inhibitor for isocitrate dehydrogenase \cite{2007_ogawa_JBacteriol}.
%AKG was modeled as an inhibitor for isocitrate lyase \cite{1988_mackintosh_BiochemJ}.
%PEP was modeled as an inhibitor for isocitrate lyase \cite{2007_ogawa_JBacteriol,1988_mackintosh_BiochemJ}.
%3PG was modeled as an inhibitor for isocitrate lyase \cite{1988_mackintosh_BiochemJ}.
%AKG was modeled as an inhibitor for malate synthase \cite{?}.
%PEP was modeled as an inhibitor for malate synthase \cite{?}.
%3PG was modeled as an inhibitor for malate synthase \cite{?}.
%Acetyl CoA was modeled as an inhibitor for malate dehydrogenase \cite{?}.
%Pyruvate was modeled as an activator for lactate dehydrogenase \cite{2008_okino_ApplMicrobiolBiotechnol}.

We added regulation to the network as informed by literature, for a total of 17 interactions.
PEP was modeled as an inhibitor for phosphofructokinase \cite{2011_cabrera_JBiolChem}, PEP carboxykinase \cite{2003_ravanal_JProteinChem}, PEP synthetase \cite{1973_chulavatnatol_JBiolChem}, isocitrate dehydrogenase \cite{2007_ogawa_JBacteriol}, isocitrate lyase \cite{2007_ogawa_JBacteriol,1988_mackintosh_BiochemJ}, and malate synthase \cite{?}, and as an activator for fructose-biphosphatase \cite{2000_donahue_JBacteriol,2006_hines_JBiolChem,2007_hines_JBiolChem}.
AKG was modeled as an inhibitor for citrate synthase \cite{1994_pereira_JBiolChem,1983_robinson_FEBSLett}, isocitrate lyase \cite{1988_mackintosh_BiochemJ}, and malate synthase \cite{?}.
3PG was modeled as an inhibitor for isocitrate lyase \cite{1988_mackintosh_BiochemJ} and malate synthase \cite{?}.
FDP was modeled as an activator for pyruvate kinase \cite{2010_zhu_Biochimie} and PEP carboxylase \cite{1972_wohl_JBiolChem}.
Pyruvate was modeled as an inhibitor for pyruvate dehydrogenase \cite{2007_kale_JBiolChem,2002_arjunan_Biochemistry} and as an activator for lactate dehydrogenase \cite{2008_okino_ApplMicrobiolBiotechnol}.
Acetyl CoA was modeled as an inhibitor for malate dehydrogenase \cite{?}.
